
\newpage
\subsection{td\_get}
\subsubsection{Declaration} Function prototype:

\begin{verbatim}
extern
int td_get
  (td_t* td, tdt_t* key, tdt_t* value, unsigned flags);
\end{verbatim}

\subsubsection{Description}


 ingroup btree

 Gets a key/value pair from a btree.

 param td Non-NULL pointer to an initialized btree structure.
 param key Non-NULL pointer to an initialized tdt.
 param value Potentially NULL pointer to a potentially uninitialized tdt.
 param flags Bits from the TDFLG\_* values.

 Note that this function will behave like cursor wrt the TDFLG\_EXACT
 and TDFLG\_PARTIAL. That is to say:

 - When TDFLG\_PARTIAL|TDFLG\_EXACT is specified, any match that is both
   partial (ie matches where the search key is smaller than or equal to
   the found key in length) and exact (ie it matches exactly for that
   length) will return zero. If such a key does not exist, it will
   return TDERR\_NOTFOUND.
 - When only TDFLG\_PARTIAL is specified, any match that is at least
   partial will return zero. If such a key does not exist, it will
   return TDERR\_NOTFOUND.
 - When only TDFLG\_EXACT is specified, the found key must match the search
   key both in length and content, and any other situation will return
   TDERR\_NOTFOUND.
 - When none of TDFLG\_EXACT or TDFLG\_PARTIAL are given, the nearest match
   will be returned. If the database is empty, TDERR\_NOTFOUND is returned.

 Also note that, since this library will never overwrite
 a given buffer's size, this poses a problem wrt partial fetches of keys:
 you will not be able to specify that you want to search partially,
 but retrieve wholly. To fix this, you must do the following:

 - Specify both TDFLG\_ALLOCKEY with the flags bitmask.
 - On successful return (and only then), the pointer in key->data will
   be the result of a call to malloc(). Obviously, key->size will represent
   the amount of malloced data.
 - After use of key->data, don't forget to free() it.

 returns Zero on success, or a TDERR\_* value on error.
 

\subsubsection{Parameters}
\subsubsection{Returns}
\subsubsection{Called by}
