
\newpage
\subsection{td\_rotate\_left}
\subsubsection{Declaration} Function prototype:

\begin{verbatim}
extern
int td_rotate_left
  (
    td_t* td,
    unsigned parentptr,
    struct keyhead* parent,
    unsigned ptr,
    struct keyhead* node
  );
\end{verbatim}

\subsubsection{Description}


 ingroup btree\_private
 Rotates the current node 'to the right' that is, toward the 'previous'
 side, because the weight at the node's 'next' pointer is bigger than
 one plus the weight at the node's 'previous' pointer.
 There are two ways in which this rotation can take place, depending
 on whether the node's next node has a previous node or not.
 
par Simple
<pre>

             Original:                       Becomes:

             parent                          parent
               |                               |
              node                           right
              /                             /   
             a    right                    node   b
                  /                       /  
                 0     b                  a    0

             Order:                          Order:

         a node right b                   a node right b

</pre>

par More Complex
<pre>

             Original:                       Becomes:

             parent                          parent
               |                               |
              node                           rightp
              /                             /   
             a    right                    node   right
                  /                       /      /  
               rightp  b                  a    c  d    b
               /   
              c     d

             Order:                          Order:

      a node c rightp d right b       a node c rightp d right b

</pre>

 Note that only 'node' and 'right' must exist; 'a', 'rightp', 'c', 'd'
 and 'b' may all be non-existent.
 Also note that only the non-single letter nodes have to be re-written
 to the dbm's resource.

 param td Non-NULL pointer to an initialized btree structure.
 param[in] parentptr Offset of the parent key node.
 param[in] parent Key header of the parent node.
 param[in] ptr Offset of the key node itself.
 param[in] node Key node itself.

 returns Zero on success, or a TDERR\_* value on error.
 

\subsubsection{Parameters}
\subsubsection{Returns}
\subsubsection{Called by}
